% \section{Bibliography}
\begin{thebibliography}{3}

\bibitem[ISO 3696]{ISO3696}
\textit{Water for analytical laboratory use -- Specification and test methods}

\bibitem[ISO 5725-1]{ISO5725-1}
\textit{Accuracy (trueness and precision) of measurement methods and results -- Part 1: General principles and definitions}

\bibitem[ISO 5725-2]{ISO5725-2}
\textit{Accuracy (trueness and precision) of measurement methods and results -- Part 2: Basic method for the determination of repeatability and reproducibility of a standard measurement method}

\bibitem[ISO 6322-1]{ISO6322-1}
\textit{Storage of cereals and pulses -- Part 1: General recommendations for the keeping of cereals}

\bibitem[ISO 6322-2]{ISO6322-2}
\textit{Storage of cereals and pulses -- Part 2: Practical recommendations}

\bibitem[ISO 6322-3]{ISO6322-3}
\textit{Storage of cereals and pulses -- Part 3: Control of attack by pests}

\bibitem[ISO 7301:2011]{ISO7301}
\textit{Rice -- Specification}

\bibitem[ISO 14864:1998]{ISO14864}
\textit{Rice -- Evaluation of gelatinization time of kernels during cooking}

\bibitem[IEC 61010-2:1998]{IEC61010-2}
\textit{Safety requirements for electric equipment for measurement, control, and laboratory use -- Part 2: Particular requirements for laboratory equipment for the heating of material}

\bibitem{ref10}
\textsc{Standard No I.C.C 167}. \textit{Determination of the protein content in cereal and cereal products for food and animal feeding stuffs according to the Dumas combustion method} (see \url{http://www.icc.or.at})

\bibitem{ref11}
Nitrogen-ammonia-protein modified Kjeldahl method -- Titanium oxide and copper sulfate catalyst. \textit{Official Methods and Recommended Practices of the AOCS} (ed. Firestone, D.E.), AOCS Official Method Ba Ai 4-91, 1997, AOCS Press, Champaign, IL

\bibitem{ref12}
\textsc{Berner D.L., \& Brown J.} Protein nitrogen combustion method collaborative study I. Comparison with Smalley total Kjeldahl nitrogen and combustion results. \textit{J. Am. Oil Chem. Soc.} 1994, \textbf{71} (11) pp 1291-1293

\bibitem{ref13}
\textsc{Buckee G.K.} Determination of total nitrogen in barley, malt and beer by Kjeldahl procedures and the Dumas combustion method -- Collaborative trial. \textit{J. Inst. Brew.} 1994, \textbf{100} (2) pp 57-64

\bibitem{ref14}
\textsc{Frister H.} \textit{Direct determination of nitrogen content by Dumas analysis; Interlaboratory study on precision characteristics}. AOAC International, Europe Section 4th International Symposium, Nyon, Switzerland, 1994, 33 pp

\bibitem{ref15}
\textsc{Ranghino F.} Evaluation of rice resistance to cooking, based on the gelatinization time of kernels. \textit{Il Riso}. 1966, \textbf{XV} pp 117-127

\bibitem{ref16}
\textsc{Tkachuk R.} Nitrogen-to-protein conversion factors for cereals and oilseed meals. \textit{Cereal Chem.} 1969, \textbf{46} (4) pp 419-423

\end{thebibliography}
